\ttitle

### 2013-07-03 Appendices/AppendixA-summaries.tex
Added stuff of survey outlier methodologies

>>>>

%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
%----------------------------------------------------------------------------------------
\section{Outlier Detection methods}
\subsection{A Survey of Outlier Detection Methodologies}
Hodge and Austin, \cite{hodge2004survey}, 2004, 734 refs.

\subsection{Summary}
This survey takes a look at different methodologies that perform outlier detection.
It gives two definitions of outliers, one of which relates to the problem statement in this thesis (taken from \cite{barnett1994outliers}):
\begin{quote}An observation (or subset of observations) which appears to be inconsistent with the remainder of that set of data.\end{quote}

The survey introduces three fundamental approaches to the problem of outlier detection:
\begin{description}
  \item[Type 1] - no prior knowledge about the data; analogous to \emph{unsupervised clustering}. Flags the remote points as outliers; mainly batch-processing systems.
  \item[Type 2] - model (and requires) both normal and abnormal data; analogous to \emph{supervised classification}. Is able to process new data online.
  \item[Type 3] - Model only normal data (and in very few cases abnormal). Generally referred to as \emph{novelty detection}, analogous to \emph{semi-supervised recognition or detection}. It only requires pre-classified normal data. It aims to define a boundary of normality.
\end{description}

The type of approaches of interest in this research is of \textbf{type 3}.
It is characterized by the ability to recognize new data as normal when it lies within the constructed boundary and as a novelty otherwise.
This ability removes the need of sample-abnormality data, which may be hard (or costly) to produce.
The method of Tax \etal \cite{tax1999supportdata} is stated to be of \textbf{type 2}, and one can argue that other methods of Tax \etal \cite{tax2001one,tax2004support} are by their one-class classification instances of \textbf{type 3} methods.

The survey states that density-based methods estimate the density distribution of the training data.
Outliers are identified as data points lying in a low-density region.
